Hydras \& Co.

### 2024-01-10 doc/hydras.tex
Changes to chapter 11; Renaming some symbols in Epsilon.E0
corrections to the general introduction

@@

\subsection{Documenting theories with \alectr}

@@

Unlike mathematical literature, where definitions and proofs are spread out over many articles and books,
the whole proof is now inside your computer. It is composed from the \texttt{.v} files you downloaded and
parts of \coq's standard library. Thus, there is no ambiguity in our definitions and the premises of the theorems. Furthermore, you will be able to navigate through the development, using your favorite text editor or IDE, and some commands like \texttt{Search}, \texttt{Locate},  etc.

@@

It may also happen that some proof looks to be useless, because the proven theorem is a trivial consequence of another (also proven) result.
For instance, let us consider the three following statements:
\begin{enumerate}
\item There is no measure into $\mathbb{N}$ for proving the termination of all hydra battles (Sect~\vref{omega-case}).
\item There is no measure into the interval\,\footnote{We use the notation $[a,b)$ for denoting the set of ordinals greater or equal than $a$ and strictly less than $b$.}  $[0,\omega^2)$ for proving the termination of all hydra battles (Sect.~\vref{omega2-case}).
\item There is no measure into $[0,\mu)$ for proving the termination of all hydra battles, for any $\mu<\epsilon_0$ (Sect.\vref{sec:free-battles-case}).
\end{enumerate}

@@

\subsubsection{Using \alectr}
Whenever possible, we use \alectr to display \coq code (definition, proof scripts) and answers.

Here are two  examples from Chapters~\ref{chapter:primrec}
and~\ref{chapter-powers}.

@@

Quotations of \coq{} source  from others libraries (\coq's standard library, borrowed plug-ins)  are displayed as follows.

@@

We use also verbatim code inclusions when the examples lead to very long computations.

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
 The present distribution has been checked with version 8.14.1 of the Coq proof assistant, with a few plug-ins. \emph{Please refer to \href{https://github.com/coq-community/hydra-battle\#readme}{the README file of the project}.}

@@

\include{chap-intro-goedel}
\include{chapter-primrec} 
\include{chapter-fol}
\include{chapter-natural-deduction}
\include{chapter-lnn-lnt}
\include{chapter-encoding}

>>>>

If a formal development is large (at least 10 KLOCs), we believe that a human-readable document containing explanations, diagrams, code snippets, examples, exercises, etc.) would be useful
for a better understanding of both the mathematical contents
and the formalization techniques used in the
development~\cite{Chiplunkar23}.

This document has been generated with \alectr (see Sect.~\vref{sect:alectryon-intro}), which ensures the \texttt{pdf} is consistent with the last compiled version of the \coq project.

@@

\subsection{Documenting theories with \alectr}
\label{sect:alectryon-intro}

@@

Unlike mathematical literature, where definitions and proofs are spread out over many articles and books,
the whole proof is now inside your computer. It is composed from the \texttt{.v} files you downloaded,
parts of \coq's standard library, and required \coq packages (see Fig.~\vref{fig:genealogy}).  Thus, there is no ambiguity in our definitions and the premises of the theorems. Furthermore, you will be able to navigate through the development, using your favorite text editor or IDE, and some commands like \texttt{Search}, \texttt{Locate},  etc.

@@

It may also happen that some direct proof looks to be useless,
because the proven theorem is a trivial consequence of another (also proven) result.
For instance, let us consider the three following statements:
\begin{enumerate}
\item There is no measure into $\mathbb{N}$ for proving the termination of all hydra battles (Sect~\vref{omega-case}).
\item There is no measure into the interval\,\footnote{We use the notation $[a,b)$ for denoting the set of ordinals greater or equal than $a$ and strictly less than $b$.}  $[0,\omega^2)$ for proving the termination of all hydra battles (Sect.~\vref{omega2-case}).
\item There is no measure into $[0,\mu)$ for proving the termination of all hydra battles, for any $\mu<\epsilon_0$ (Sect.\vref{sec:free-battles-case}).
\end{enumerate}

@@

\subsubsection{Using \alectr}
Whenever possible, we use \alectr to display \coq code (definition, proof scripts) and answers.
Here are two  examples from Chapters~\ref{chapter:primrec}
and~\ref{chapter-powers}.

@@

Quotations of \coq{} source  from other libraries (\coq's standard library, borrowed plug-ins)  are displayed as follows.

@@

We use also verbatim code inclusions when the examples lead to too long computations.

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
 The present distribution has been checked with versions up to 8.18 of the Coq proof assistant, with a few plug-ins. \emph{Please refer to \href{https://github.com/coq-community/hydra-battle\#readme}{the README file of the project}.}

@@

\include{chap-intro-goedel}
\include{chapter-primrec} 
\include{chapter-fol}
\include{chapter-natural-deduction}
\include{chapter-lnn-lnt}
\include{chapter-encoding}
\include{chapter-expressible}
